Capstone Movielens Report

### 2025-11-28 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section are available in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) script on _GitHub_.
:::

>>>>

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UME Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
:::

### 2025-11-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.

We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).

@@

Let's visualize the fine-tuning results:
```{r}
UMGE.rglr.fine_tune.results$tuned.result |>
  data.plot(title = "UMGE Model Regularization: Fine-tuned result",
              xname = "parameter.value",
              yname = "RMSE",
              xlabel = TeX(r'[$\lambda$]'),
              ylabel = str_glue("Deviation from the best RMSE value (",
                                as.character(round(UMGE.rglr.fine_tune.RMSE.best, digits = 7)),
                                ")"),
              normalize = TRUE)
```
\newpage

>>>>

@@

Let's visualize the fine-tuning results:
```{r}
UMGE.rglr.fine_tune.results$tuned.result |>
  data.plot(title = "UMGE Model Regularization: Fine-tuned result",
              xname = "parameter.value",
              yname = "RMSE",
              xlabel = TeX(r'[$\lambda$]'),
              ylabel = str_glue("Deviation from the best RMSE value (",
                                as.character(round(UMGE.rglr.fine_tune.RMSE.best, digits = 7)),
                                ")"),
              normalize = TRUE)
```

::: {.noteblock data-latex=""}
Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
:::
